### 2019-09-27 boek.tex
update
restructure repository

\documentclass[10pt]{book}

@@

% scripting packages
\usepackage{blindtext}

@@

% figure packages
\usepackage{tikz}
\usetikzlibrary{calc,shapes,arrows,intersections,shadows}
\tikzset{>=latex}
\usepackage{graphicx}
\usepackage[indention=0.5cm,labelsep=colon,font={sf,small},labelfont={bf,sf}]{caption}
\usepackage[indention=0.5cm,font={sf,small},labelfont={bf,sf}]{subcaption}
\usepackage{float}
\usepackage{multirow}
\usepackage{import}
\usepackage{xcolor}
\usepackage{colortbl}

@@

% boxes around sections
\usepackage{tcolorbox}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{dyno: A toolkit for inferring and interpreting trajectories} 
\chaptermark{dyno: A toolkit for inferring and interpreting trajectories.} % short title
\label{chap:dyno}
\begin{quote}
	\textbf{Abstract:} \blindtext
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., and Saeys, Y. dyno: A toolkit for inferring and interpreting trajectories. \textit{Journal} vol, issue (2019), page--page. doi.
\include{ch4_dyno/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH5: SCORPIUS       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{SCORPIUS: Fast, accurate, and robust single-cell pseudotime} 
\chaptermark{SCORPIUS: Fast, accurate, and robust single-cell pseudotime.} % short title
\label{chap:scorpius}
\begin{quote}
	\textbf{Abstract:} \blindtext
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., Sichien, D., Tavernier, S., Janssens, S. Guilliams, M., Lambrecht, B., De Preter, K., and Saeys, Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. \textit{Journal} vol, issue (2019), page--page. \doi{10.1101/079509v2}.
\newpage
\graphicspath{{./ch5_scorpius/}}
\include{ch5_scorpius/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH6: BRED         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{bred: Inferring single cell regulatory networks} 
\chaptermark{bred: Inferring single cell regulatory networks.} % short title
\label{chap:bred}
\begin{quote}
	\textbf{Abstract:} \blindtext
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., and Saeys, Y. Inferring Single Cell Regulatory Networks. \textit{Journal} vol, issue (2019), page--page. doi.
\newpage
\include{ch6_bred/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH7: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{incgraph: Optimising regulatory networks} 
\chaptermark{incgraph: Optimising regulatory networks.} % short title
\label{chap:incgraph}
\graphicspath{{./ch7_incgraph/}}
\begin{quote}
	\textbf{Abstract:} Graphlets are small network patterns that can be counted in order to characterise the structure of a network (topology).
	As part of a topology optimisation process, one could use graphlet counts to iteratively modify a network and keep track of the graphlet counts, in order to achieve certain topological properties.
	Up until now, however, graphlets were not suited as a metric for performing topology optimisation; when millions of minor changes are made to the network structure it becomes computationally intractable to recalculate all the graphlet counts for each of the edge modifications. \\ IncGraph is a method for calculating the differences in graphlet counts with respect to the network in its previous state, which is much more efficient than calculating the graphlet occurrences from scratch at every edge modification made.
	In comparison to static counting approaches, our findings show IncGraph reduces the execution time by several orders of magnitude.
	The usefulness of this approach was demonstrated by developing a graphlet-based metric to optimise gene regulatory networks.
	IncGraph is able to quickly quantify the topological impact of small changes to a network, which opens novel research opportunities to study changes in topologies in evolving or online networks, or develop graphlet-based criteria for topology optimisation. \\
	IncGraph is freely available as an open-source R package on CRAN (incgraph). The development version is also available on GitHub (\href{http://www.github.com/rcannood/incgraph}{rcannood/incgraph}).
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Ruyssinck, J., Ramon, J., De Preter, K., and Saeys, Y. IncGraph: Incremental graphlet counting for topology optimisation. \textit{PLOS ONE} 13, 4 (2018), e0195997. \doi{10.1371/journal.pone.0195997}.
\newpage
\include{ch7_incgraph/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH8: Guidelines       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Essential guidelines for computational method benchmarking} 
\chaptermark{Essential guidelines for computational method benchmarking.} % short title
\label{chap:guidelines}
\graphicspath{{./ch8_guidelines/}}
\begin{quote}
	\textbf{Abstract:} In computational biology and other sciences, researchers are frequently faced with a choice between several computational methods for performing data analyses. Benchmarking studies aim to rigorously compare the performance of different methods using well-characterized benchmark datasets, to determine the strengths of each method or to provide recommendations regarding suitable choices of methods for an analysis. However, benchmarking studies must be carefully designed and implemented to provide accurate, unbiased, and informative results. Here, we summarize key practical guidelines and recommendations for performing high-quality benchmarking analyses, based on our experiences in computational biology.
\end{quote}
\vfill
Adapted from:\\
Weber, L. M., Saelens W., \textbf{Cannoodt, R.}, Soneson, C., Hapfelmeier, A., Gardner, P. P.,
Boulesteix, A., Saeys, Y., and Robinson, M. D.. 
Essential guidelines for computational method benchmarking. \textit{Genome Biology} 20, 125 (2019). \doi{10.1186/s13059-019-1738-8}.
\newpage
\include{ch8_guidelines/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%      CH8: DISCUSSION      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Discussion and Future Perspectives} 
\chaptermark{Discussion and Future Perspectives.} % short title
\label{chap:discussion}
\include{ch8_discussion/content}

>>>>

\PassOptionsToPackage{table}{xcolor}
\documentclass[10pt]{book}

@@

@@

% figure packages
\usepackage{tikz}
\usetikzlibrary{calc,shapes,arrows,intersections,shadows}
\tikzset{>=latex}
\usepackage{graphicx}
\usepackage[indention=0.5cm,labelsep=colon,font={sf,small},labelfont={bf,sf}]{caption}
\usepackage[indention=0.5cm,font={sf,small},labelfont={bf,sf}]{subcaption}
\usepackage{float}
\usepackage{multirow}
\usepackage{import}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{tcolorbox}

@@

% allow to adjust spacing in enumerates and itemizes
\usepackage{enumitem}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage{\thispagestyle{empty}\cleardoublepage}
%\chapter{dyno: A toolkit for inferring and interpreting trajectories} 
%\chaptermark{dyno: A toolkit for inferring and interpreting trajectories.} % short title
%\label{chap:dyno}
%\begin{quote}
%	\textbf{Abstract:} 
%\end{quote}
%\vfill
%Adapted from:\\
%\textbf{Cannoodt, R.}, Saelens, W., and Saeys, Y. dyno: A toolkit for inferring and interpreting trajectories. \textit{Journal} vol, issue (2019), page--page. doi.
%\include{ch4_dyno/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH4: SCORPIUS       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{SCORPIUS: Fast, accurate, and robust single-cell pseudotime} 
\chaptermark{SCORPIUS: Fast, accurate, and robust single-cell pseudotime.} % short title
\label{chap:scorpius}
\begin{quote}
	\textbf{Abstract:}
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., Sichien, D., Tavernier, S., Janssens, S. Guilliams, M., Lambrecht, B., De Preter, K., and Saeys, Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. \textit{Journal} vol, issue (2019), page--page. \doi{10.1101/079509v2}.
\newpage
\graphicspath{{./ch4_scorpius/}}
\include{ch4_scorpius/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH5: BRED         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{bred: Inferring single cell regulatory networks} 
\chaptermark{bred: Inferring single cell regulatory networks.} % short title
\label{chap:bred}
\begin{quote}
	\textbf{Abstract:}
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., and Saeys, Y. Inferring Single Cell Regulatory Networks. \textit{Journal} vol, issue (2019), page--page. doi.
\newpage
\include{ch5_bred/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH5B: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{incgraph: Optimising regulatory networks} 
\chaptermark{incgraph: Optimising regulatory networks.} % short title
\label{chap:incgraph}
\graphicspath{{./ch5b_incgraph/}}
\begin{quote}
	\textbf{Abstract:} Graphlets are small network patterns that can be counted in order to characterise the structure of a network (topology).
	As part of a topology optimisation process, one could use graphlet counts to iteratively modify a network and keep track of the graphlet counts, in order to achieve certain topological properties.
	Up until now, however, graphlets were not suited as a metric for performing topology optimisation; when millions of minor changes are made to the network structure it becomes computationally intractable to recalculate all the graphlet counts for each of the edge modifications. \\ IncGraph is a method for calculating the differences in graphlet counts with respect to the network in its previous state, which is much more efficient than calculating the graphlet occurrences from scratch at every edge modification made.
	In comparison to static counting approaches, our findings show IncGraph reduces the execution time by several orders of magnitude.
	The usefulness of this approach was demonstrated by developing a graphlet-based metric to optimise gene regulatory networks.
	IncGraph is able to quickly quantify the topological impact of small changes to a network, which opens novel research opportunities to study changes in topologies in evolving or online networks, or develop graphlet-based criteria for topology optimisation. \\
	IncGraph is freely available as an open-source R package on CRAN (incgraph). The development version is also available on GitHub (\href{http://www.github.com/rcannood/incgraph}{rcannood/incgraph}).
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Ruyssinck, J., Ramon, J., De Preter, K., and Saeys, Y. IncGraph: Incremental graphlet counting for topology optimisation. \textit{PLOS ONE} 13, 4 (2018), e0195997. \doi{10.1371/journal.pone.0195997}.
\newpage
\include{ch5b_incgraph/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%      CH6: DISCUSSION      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Discussion} 
\chaptermark{Discussion.} % short title
\label{chap:discussion}
\graphicspath{{./ch6_discussion/}}
\include{ch6_discussion/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   CH7: Self-assessment    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Self-assessment in trajectory inference} 
\chaptermark{Self-assessment in trajectory inference.} % short title
\label{chap:selfassessment}
\graphicspath{{./ch7_selfassessment/}}
%\begin{quote}
%	\textbf{Abstract:}
%\end{quote}
%\vfill
%Adapted from:\\
%Weber, L. M., Saelens W., \textbf{Cannoodt, R.}, Soneson, C., Hapfelmeier, A., Gardner, P. P.,
%Boulesteix, A., Saeys, Y., and Robinson, M. D.. 
%Essential guidelines for computational method benchmarking. \textit{Genome Biology} 20, 125 (2019). \doi{10.1186/s13059-019-1738-8}.
\newpage
\include{ch7_selfassessment/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH8: Guidelines       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Essential guidelines for computational method benchmarking} 
\chaptermark{Essential guidelines for computational method benchmarking.} % short title
\label{chap:guidelines}
\graphicspath{{./ch8_guidelines/}}
\begin{quote}
	\textbf{Abstract:} In computational biology and other sciences, researchers are frequently faced with a choice between several computational methods for performing data analyses. Benchmarking studies aim to rigorously compare the performance of different methods using well-characterized benchmark datasets, to determine the strengths of each method or to provide recommendations regarding suitable choices of methods for an analysis. However, benchmarking studies must be carefully designed and implemented to provide accurate, unbiased, and informative results. Here, we summarize key practical guidelines and recommendations for performing high-quality benchmarking analyses, based on our experiences in computational biology.
\end{quote}
\vfill
Adapted from:\\
Weber, L. M., Saelens W., \textbf{Cannoodt, R.}, Soneson, C., Hapfelmeier, A., Gardner, P. P.,
Boulesteix, A., Saeys, Y., and Robinson, M. D. 
Essential guidelines for computational method benchmarking. \textit{Genome Biology} 20, 125 (2019). \doi{10.1186/s13059-019-1738-8}.
\newpage
\include{ch8_guidelines/content}
